---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r badges, echo = FALSE}
badge_stars <- function(color = "green", url = NULL, cookie = Sys.getenv("ADVENT_COOKIE_2023")) {
  
  req <- httr::GET(
    glue::glue('https://adventofcode.com/'),
    httr::add_headers(
      .headers = c(
        "user-agent" = "Mozilla/5.0 (X11; Linux x86_64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/87.0.4280.88 Safari/537.36",
        "cookie" = paste0("session=", cookie)
        )
      )
    )
  
  parsed <- xml2::read_html(req)
  stars <- rvest::html_node(parsed, ".user")
  star_text <- rvest::html_text(stars)
  badge <- paste0("![](https://img.shields.io/badge/", "2023 star count", "-", star_text, "-", color, ".svg)")
  
  if (is.null(url))
    return(badge)
  
  paste0("[", badge, "](", url, ")")
}
```

# Advent of Code

<!-- badges: start -->
`r badge_stars()`
<!-- badges: end -->

This repo contains all of my Advent of Code solutions using R. I'm using this to practice programming and problem-based solutions, but it's mostly for a little holiday fun. I'm also using a custom repo badge that scrapes a user's Advent of Code star count and displays it as a badge.

## Solutions so far
### [2023](R/2023) | [2022](R/2022) | [2021](R/2021) | [2020](R/2020)

| Day | Puzzle | Solution | Data |
| :---: | :---: | :---: | :---: | 
| 1 | [TBD](https://adventofcode.com/2023/day/1) | [R](R/2023/day01.R) | [Puzzle input](data/2023/day01.txt)
